\documentclass[11pt]{article}
\begin{document}
\section{The 6 most common SDLC models:}

Waterfall is a model that does not allow for the revision of a previous phase in the cycle. This model will not be used as a delay in one phase will have a domino effect on all following phases and therefor one member that does not work effectively will hold back the others.

V shaped model is an adaptation of waterfall that has testing done at the end of each phase to prevent errors/discrepancies before moving on to the following phase. This model will not be used for the same reason as the waterfall model

Iterative model allows for a quick production of a single version on a certain set of requirements and allows for a simple means to implement changes.

Spiral is an adaptation of the iterative model that will run multiple cycles before the project is complete. Suffers the drawback that it may be drawn into an infinite spiral

Big bang model is a haphazard methodology that no planning is done. This is normally used when the requirements are not completely understood by the client or the developer. This will not be used as it is only usable in small groups of programmers (1 or 2) and on small scale projects.

Agile model is a further adaptation onto the Iterative model that still produces a product very quickly but involves the client and user more regularly to ensure it is meeting the expectations. The main drawback to Agile is because of the user centered approach the user may lead the project astray if they are not clear.

We will be using an agile approach as it is the current industry standard and we believe it will allow us to bring the most effective product in the end, especially considering on the wide variety of people that out project will be appealing to.

\section{Supporting Software}
	\subsection{Google Places API} 
	This will be used to locate all places of interest in a certain area such as hospitals, schools, airports, etc. This will be necessary as producing a list of all the places on interest accurately is not viable.
	
\end{document}