\documentclass[11pt]{article}
\usepackage{graphicx}
\usepackage{enumerate}
\graphicspath{{./}}

\begin{document}
	\title{
		COMS3002 - Software Engineering\\
		\large Use Case Realisation
	}
	\author{Aobakwe Mosweu (1049090), \\Seale Rapolai (1098005)}
	\maketitle
	
	\clearpage
	\tableofcontents
	\clearpage
	
	\section{Introduction}
	\begin{flushleft}
		This document will include a partially dressed use case description of the vital use cases of each subsystem, that is for Customers, REBrokers, REManagers. This document should describe in depth each use case. It should be such that using this information alone should be enough to identiry which what the the systems functionalities are and how the various functionalities interact with each other. These descriptions will include use case ID, name, scope, trigger event, description, actors, related use cases, pre-conditions and post-conditions. These uses cases will form the foundation upon which the entire system will be build.
	\end{flushleft}
	
	\section{Customer}
	\begin{flushleft}
		The following are the descriptions of all the vital use cases that the customer will interact with. 
	\end{flushleft}
	
		\subsection{Customer Account}
		
		\subsection{Customer Preferance List}
		
		\subsection{Customer Home Suggestions}
		
		\subsection{Customer Home Viewings}

	\section{REBroker}
	\begin{flushleft}
		The following are the descriptions of all the vital use cases that the REBroker will interact with. 
	\end{flushleft}
		
		\subsection{REBroker Account}
		
		\subsection{Client List}
		
		\subsection{Client Home List}
		
		\subsection{Property Status}
		
		\subsection{Viewing Time}
		
		\subsection{}
		
		\begin{enumerate}[i]
			\item \textbf{Client Preference Importance}
			\begin{itemize}
				\item View Client Prefence Importance (REB-I01)
				\item Update Client Prefence Importance (REB-I02)
			\end{itemize}
		\end{enumerate}
	
	\section{REManager}
	\begin{flushleft}
		The following are the descriptions of all the vital use cases that the REManager will interact with. 
	\end{flushleft}
		
		\subsection{REManager Account}
		
		\subsection{Application Management}
		
		\subsection{Employee Management}
		
		\subsection{Transaction Management}
		
		\subsection{Finantial Statement}
	
		\begin{enumerate}[i]
			\item \textbf{Statistic Reports}
			\begin{itemize}
				\item Create Report (REM-I01)
				\item View Report (REM-I02)
				\item Update/Modify Report (REM-I03)
				\item Delete Report (REM-I04)
			\end{itemize}
			
			\item \textbf{Report Graphs}
			\begin{itemize}
				\item Create Graph (REM-J01)
				\item View Graph (REM-J01)
				\item Update/Modify Graph (REM-J01)
				\item Delete Graph (REM-J01)
			\end{itemize}
			
			\item \textbf{Budger History}
			\begin{itemize}
				\item View Past Bugdets
				\item Restore Budget
			\end{itemize}
			
		\end{enumerate}
	
	\section{Conclutions}
	
	
\end{document}
