\documentclass[11pt]{article}
\usepackage{graphicx}
\usepackage{enumerate}
\graphicspath{{./}}

\begin{document}
	\title{
		COMS3002 - Software Engineering\\
		\large Use Case Realisation
	}
	\author{Aobakwe Mosweu (1049090), \\Seale Rapolai (1098005)}
	\maketitle
	
	\clearpage
	\tableofcontents
	\clearpage
	
	\section{Use Case List}
	\begin{flushleft}
		This section will contain a list of all the use cases identified using the user stories defined earlier in the sprint. The list of use cases below will be divided into three categories, namely:
	\end{flushleft}
	\begin{itemize}
		\item \textbf{Vital}: use cases that are vital to the system to function.
		\item \textbf{Complementary}: use cases that support and enhance the system but are not very vital to the system's operation.
		\item \textbf{Fluff}: use cases that enhance the system and improving the user experience.
	\end{itemize}
	
		\subsection{Customer}
		\begin{flushleft}
			The following is a list of all use cases that are related to the customer. That is, the use cases that the customer will interact with.
		\end{flushleft}
	
			\subsubsection{Vital}
				\begin{enumerate}[i]
					\item \textbf{Customer Account}
					\begin{itemize}
						\item Create Account (CT-A01)
						\item View Account Details (CT-A02)
						\item Update Account Details (CT-A03)
						\item Delete Account (CT-A04)
					\end{itemize}
					
					\item \textbf{Customer Preferance List}
					\begin{itemize}
						\item Create Home Preference List (CT-B01)
						\item View Home Prefenrence List (CT-B02)
						\item Update Home Prefenrence List (CT-B03)
						\item Delete Home Prefenrence List (CT-B04)
					\end{itemize}
					
					\item \textbf{Customer Home Suggestions}
					\begin{itemize}
						\item View Suggested Homes (CT-C01)
						\item Delete Suggested Home (CT-C02)
					\end{itemize}
					
					\item \textbf{Customer Home Viewings}
					\begin{itemize}
						\item Create Viewing Time (CT-D01)
						\item View Viewing Time (CT-D02)
						\item Update Viewing Time (CT-D03)
						\item Delete Viewing Time (CT-D04)
					\end{itemize}
				\end{enumerate}
	
			\subsubsection{Complementary}
				\begin{enumerate}[i]
					\item \textbf{Customer Preference Comment}
					\begin{itemize}
						\item Create Prefence Comment (CT-E01)
						\item View Prefence Comment (CT-E02)
						\item Update Prefence Comment (CT-E03)
						\item Delete Prefence Comment (CT-E04)
					\end{itemize}
					
					\item \textbf{Home Availability/Status}
					\begin{itemize}
						\item Create (Add) Available Homes (CT-F01)
						\item View Home Availability (CT-F02)
						\item Delete Unavailable Homes (CT-F03)
					\end{itemize}
				\end{enumerate}
		
			\subsubsection{Fluff}
				\begin{enumerate}[i]
					\item \textbf{Customer Search Histomer}
					\begin{itemize}
						\item Create Search History (CT-G01)
						\item View Search History (CT-G02)
						\item Update Search History (CT-G03)
						\item Delete Search History (CT-G04)
					\end{itemize}
					
					\item \textbf{Customer Bond Calculation}
					\begin{itemize}
						\item Create Bond Calculation (CT-H01)
						\item View Bond Calculation (CT-H02)
						\item Update Bond Calculation (CT-H03)
						\item Delete Bond Calculation (CT-H04)
					\end{itemize}
					
					\item \textbf{Home Search Advice}
					\begin{itemize}
						\item View Home Search Advice (CT-I01)
					\end{itemize}
				\end{enumerate}
		

		\subsection{REBroker}
		
		\subsection{REManager}
	
	\section{Partail dresses Use Case Descrition}
	\begin{flushleft}
		This section will incluse a partialy dressed use case description of the vital use cases as listed in the above section. This description will include use case ID, name, scope, trigger event, description, actors, related use cases, Pre-conditions and post-conditions.
	\end{flushleft}
\end{document}
